---
title: "MIXED EFFECT MODEL WP1"
output: html_document
date: '2022-07-19'
---

## 1. SETUP

```{r include=FALSE}
# 1. SETUP ----------------------------------------------------------------------
# PACKAGES
library(tidyverse)  # process data frame
library(readr)      # process rds, csv 
library(lubridate)  # process time
library(readxl)     # read xlsx

library(lme4)       # fit model
library(AICcmodavg) # calculate AIC
library(effects)    # display effect
library(lattice)    # visualize data

#library(INLA)       # INLA model

# FUNCTION
MyStd <- function(x) { (x - mean(x)) / sd(x)} #- function to standardize
c. <- function (x) scale(x, scale = FALSE) 
```

## 2. LOAD DATA

```{r}
dir_otl <- "D:/OneDrive - UGent/FWO/@FWO/05_MSc thesis/2022_Kelly/git_kelly/data" 
otl <- read_rds(file.path(dir_otl, "otl_8ab_full for analysis_130223.rds"))
otl <- otl %>% filter(AnnulusDiameterIncrement.um > 0) #1 point = 0

#otl <- otl %>% mutate(Yearclass = SamplingYear - AgeAtCapture) #somehow lost Yearclass in previous coding but not time to check
###covert Year and Cohort variables into factors
otl <- otl %>% mutate(Year = GrowingYear,
                      Cohort = Yearclass,
                      fGrowingYear = factor(GrowingYear),
                      fYearclass   = factor(Yearclass))

```

## 3. ANALYZE DATA

Model: **log(AnnulusDiameterIncrement.um) \~ Intrinsic Effects + Extrinsic Effects + Random Effects**

Intrinsic Effects:

-   Age

-   AgeAtCapture

Extrinsic Effects:

-   SeaBottomTemperature

-   FishingMortality

-   StockBiomass

Random effects:

-   FishID

-   GrowingYear

-   Yearclass

### 3.1. 8ab

```{r}
data <- otl

# check number of increment per GrowingYear
data_sum <- data %>% group_by(GrowingYear) %>% summarize(n_increment = n())

#data <- otl %>% filter(GrowingYear >= 2007, GrowingYear <= 2016) #only >20 increment years
```

Note: mention the correlation between fixed effects

Sample size:

-   Number of sampled fish: 852, Age At Capture: 3-25

-   Sampling Year: 1960 - 2020

-   Growing Year: 1958 - 2019, Yearclass: 1957 - 2017

```{r}
# Sampling size
n_distinct(data$FishID) #181
sort(unique(data$SamplingYear)) #2008 - 2020
sort(unique(data$GrowingYear)) #2003 - 2019
sort(unique(data$Yearclass)) #1997 - 2016
summary(data$Age) #1-14
summary(data$AgeAtCapture) #3-14

# AgeAtCapture vs SamplingYear
data_sum_year <- data %>% group_by(IcesAreaGroup, SamplingYear, AgeAtCapture, FishID) %>% summarize(n = n()) %>% group_by(IcesAreaGroup, SamplingYear, AgeAtCapture) %>% summarize(NumberFishSampled = n())

ggplot(data = data_sum_year, aes(x = SamplingYear, y = AgeAtCapture, size = NumberFishSampled)) + geom_point(alpha = 0.5) + 
  facet_wrap(~ IcesAreaGroup) + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank()) +
  ylim(3,15)

# AgeAtCapture vs Yearclass
data_sum_yearclass <- data %>% group_by(IcesAreaGroup, Yearclass, AgeAtCapture, FishID) %>% summarize(n = n()) %>% group_by(IcesAreaGroup, Yearclass, AgeAtCapture) %>% summarize(NumberFishSampled = n())

ggplot(data = data_sum_yearclass, aes(x = Yearclass, y = AgeAtCapture, size = NumberFishSampled)) + geom_point(alpha = 0.5) + 
  facet_wrap(~ IcesAreaGroup) + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank()) +
  ylim(3,15)

```

#### 3.1.1. Random effect structure

Fit the maximal intrinsic structure: Age + AgeAtCapture then eventuall find the optimal random effect structure

##### FishID and DataSource

```{r}
# Age slope
data$clogAge <- as.vector(c.(log(data$Age)))
data$clogAAC <- as.vector(c.(log(data$AgeAtCapture)))

ggplot(data = data, aes(x = Age, y = log(AnnulusDiameterIncrement.um))) + geom_point()
ggplot(data = data, aes(x = log(Age), y = log(AnnulusDiameterIncrement.um))) + geom_point()
ggplot(data = data, aes(x = c.(log(Age)) , y = log(AnnulusDiameterIncrement.um))) + geom_point()
```

```{r warning=FALSE}
# Fit model - iid intercept FishID vs Age slope and intercept FishID
M1a <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1|FishID), data)
M1b <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID), data)

# Model comparison
models<-list(M1a, M1b)
Modnames <- c('M1a', 'M1b')
aictab(cand.set = models, modnames = Modnames, sort = TRUE)
```

Best FishID structure: random slope and intercept for Age, FishID

##### GrowingYear and Yearclass

Fit model with GrowingYear/Yearclass only to find the trend in GrowingYear/Yearclass

```{r}
# Fit model 

# Intercept
M2a <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + (1|fGrowingYear), data)
M2b <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + (1|fYearclass), data)

M3a <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + (1 + clogAge|fGrowingYear), data)
M3b <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + (1 + clogAge|fYearclass), data)

# Model comparison
models<-list(M2a, M2b, M3a, M3b)
Modnames <- c('M2a', 'M2b', 'M3a', 'M3b')
aictab(cand.set = models, modnames = Modnames, sort = TRUE)
```

Best GrowingYear structure: random slope and intercept for Age, FishID, GrowingYear (Age\|FishID), (Age\|GrowingYear)

Best Yearclass structure: random slope and intercept for Age, FishID, Yearclass (Age\|FishID), (Age\|Yearclass)

###### **Visualize the GrowingYear**

M3test2 \<- lmer(log(AnnulusDiameterIncrement.um) \~ c.(Age) + c.(AgeAtCapture) + (1\|FishID) + (1\|fGrowingYear), data)

```{r}
# Growing Year

# extract random effect interecept, slope from the model
GrowingYear.df <- ranef(M3a)$fGrowingYear

GrowingYear.df <- GrowingYear.df %>% 
  mutate(GrowingYear = as.numeric(rownames(GrowingYear.df)),
         Intercept = `(Intercept)`,
         Slope = clogAge,
         RandomEffect.se = sqrt(attr(ranef(M3a,postVar=TRUE) [["fGrowingYear"]],"postVar")[1,1,])) 

# create dataframe with random effect by age
#GrowingYear.df <- as.tibble(sapply(GrowingYear.df, rep.int, times=length(list_clogAge)))
GrowingYear.df <- GrowingYear.df %>% 
  mutate(RandomEffect.Intercept = Intercept,
         RandomEffect.Intercept.upper = RandomEffect.Intercept + RandomEffect.se,
         RandomEffect.Intercept.lower = RandomEffect.Intercept - RandomEffect.se,
         ) 
                                    


# Plot Interecept
ggplot() + 
  geom_ribbon(data = GrowingYear.df, 
              aes(x = GrowingYear,
                  ymax = RandomEffect.Intercept.upper,
                  ymin = RandomEffect.Intercept.lower), 
              fill = 'grey70') +
  geom_line(data = GrowingYear.df, 
            aes(x = GrowingYear, 
                y = RandomEffect.Intercept)) +
  geom_line(aes(x = data$GrowingYear, y = 0), 
            linetype="dashed") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank()) +
  #ggtitle("Year random effect") +
  xlab("Year") +
  ylab("Year random effect")



```

###### **Compare Temporal trend with extrinsic variables**

p.adult

```{r}
library(patchwork)

p.year.adult<- ggplot() +
  geom_ribbon(data = GrowingYear.df, 
              aes(x = GrowingYear,
                  ymax = RandomEffect.Intercept.upper,
                  ymin = RandomEffect.Intercept.lower),
              fill = '#01665e',
              alpha = 0.3) +
  geom_line(data = GrowingYear.df, 
            aes(x = GrowingYear, 
                y = RandomEffect.Intercept),
            color = '#01665e') +
  geom_line(aes(x = GrowingYear.df$GrowingYear, y = 0), 
            linetype = "dashed",
            color = "grey70") +
  theme_classic() +
  theme(axis.title = element_blank()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank()) +
  theme(legend.position = "top") +
  ggtitle("Year effect") +
  xlim(2003, 2019)
  

# Temperature
p.temp.adult <- ggplot() + 
  geom_line(data = data, 
            aes(x = GrowingYear, 
                y = SeaBottomTemperature.degC),
            color = '#01665e') +
  theme_classic() +
  theme(axis.title = element_blank()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank()) +
  ggtitle("Sea Bottom Temperature (degC)") +
  xlim(2003, 2019)

# Fishing mortality
p.f.adult <- ggplot() + 
  geom_line(data = data, 
            aes(x = GrowingYear, 
                y = FishingMortality),
            color = '#01665e') +
   theme_classic() +
  theme(axis.title = element_blank()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank()) +
  ggtitle("Fishing Mortality") +
  xlim(2003, 2019)

# Stockbiomass
p.sb.adult <- ggplot() + 
  geom_line(data = data, 
            aes(x = GrowingYear, 
                y = SpawningStockBiomass.1000t),
            color = '#01665e') +
  theme_classic() +
  theme(axis.title = element_blank()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank()) +
  ggtitle("Spawning Stock Biomass (1000t)") +
  xlim(2003, 2019)


# Plot by Maturity
p.adult <- p.year.adult/p.temp.adult/p.f.adult/p.sb.adult + theme(plot.title = element_text(face = "bold"))
p.adult
```

###### **Visualize the Yearclass effect**

```{r}
# Growing Year
# create dataframe with random effect by age
#GrowingYear.df <- as.tibble(sapply(GrowingYear.df, rep.int, times=length(list_clogAge)))
GrowingYear.df <- GrowingYear.df %>% 
  mutate(RandomEffect.Intercept = Intercept,
         RandomEffect.Intercept.upper = RandomEffect.Intercept + RandomEffect.se,
         RandomEffect.Intercept.lower = RandomEffect.Intercept - RandomEffect.se,
         ) 

# extract random effect interecept, slope from the model
Yearclass.df <- ranef(M3b)$fYearclass

Yearclass.df <- Yearclass.df %>% 
  mutate(Yearclass = as.numeric(rownames(Yearclass.df)),
         Intercept = `(Intercept)`,
         Slope = clogAge,
         RandomEffect.se = sqrt(attr(ranef(M3b,postVar=TRUE) [["fYearclass"]],"postVar")[1,1,])) 

# create dataframe with random effect by age
Yearclass.df <- Yearclass.df %>% 
  mutate(
         RandomEffect.Intercept = Intercept,
         RandomEffect.Intercept.upper = RandomEffect.Intercept + RandomEffect.se,
         RandomEffect.Intercept.lower = RandomEffect.Intercept - RandomEffect.se
         ) 
                                    


# Plot Interecept
ggplot() + 
  geom_ribbon(data = Yearclass.df, 
              aes(x = Yearclass,
                  ymax = RandomEffect.Intercept.upper,
                  ymin = RandomEffect.Intercept.lower), 
              fill = 'grey70') +
  geom_line(data = Yearclass.df, 
            aes(x = Yearclass, 
                y = RandomEffect.Intercept)) +
  geom_line(aes(x = data$Yearclass, y = 0), 
            linetype="dashed") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank()) +
  ggtitle("Yearclass random effect - Intercept") +
  xlab("Yearclass") +
  ylab("Yearclass random effect - Intercept")

```

The Yearclass effect is contrast to that of GrowingYear, both in terms of Intercept and by age. This might be due to a mechanism in the growth of sole, also observed in cod (Denechaude 2020).

**Models with both GrowingYear and Yearclass**

```{r warning=FALSE}
# GrowingYear + Yearclass 
M4a <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (clogAge|FishID) + (1|fGrowingYear) + (1|fYearclass), data)
M4b <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (clogAge|FishID) + (clogAge|fGrowingYear) + (1|fYearclass), data)
M4c <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (clogAge|FishID) + (1|fGrowingYear) + (clogAge|fYearclass), data)
M4d <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (clogAge|FishID) + (clogAge|fGrowingYear) + (clogAge|fYearclass), data)

# Model comparison
models <- list(M2a, M2b, M3a, M3b, M4a, M4b, M4c, M4d)
Modnames <- c('M2a', 'M2b', 'M3a', 'M3b', 'M4a', 'M4b', 'M4c', 'M4d')
aictab(cand.set = models, modnames = Modnames, sort = TRUE)
```

Best random effect structure: random slope and intercept for Age, FishID, GrowingYear - (Age\|FishID), (Age\|GrowingYear)

#### 3.1.2. Intrinsic structure

```{r}
# GrowingYear + Yearclass 
M3a1 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + (1 + clogAge|FishID) + (1 + clogAge|fGrowingYear), data)

M3a2 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + (1 + clogAge|fGrowingYear), data)

# Model comparison
models <- list(M3a1, M3a2)
Modnames <- c('M3a1', 'M3a2')
aictab(cand.set = models, modnames = Modnames, sort = TRUE)

```

Best random effect structure + intrinsic structure: random slope and intercept for Age, FishID, GrowingYear, Yearclass - (Age\|FishID), (Age\|DataSource), (Age\|GrowingYear), (Age\|Yearclass) + Age, AgeAtCapture

Intrinsic effects:

-   Age

#### 3.1.3. Extrinsic structure

FishingMortality + (Age\|FishID) + (Age\|fGrowingYear) + (Age\|fYearclass), data)

M4d3 \<- lmer(log(AnnulusDiameterIncrement.um) \~ Age + SeaBottomTemperature.degC + FishingMortality + SpawningStockBiomass.1000t + (Age\|FishID) + (Age\|fGrowingYear) + (Age\|fYearclass), data)

M4d11 \<- lmer(log(AnnulusDiameterIncrement.um) \~ Age + FishingMortality\*clogAge + (Age\|FishID) + (Age\|fGrowingYear) + (Age\|fYearclass), data)

```{r}
# Temperature, FishingMortality.juv2, StockBiomassAtMaturity, MaturityStage

# 1 var
M3a4 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC + (1 + clogAge|fGrowingYear), data)

M3a5 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + FishingMortality + (1 + clogAge|fGrowingYear), data)

M3a6 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SpawningStockBiomass.1000t + (1 + clogAge|fGrowingYear), data)

# 2 vars
M3a7 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC + FishingMortality + (1 + clogAge|fGrowingYear), data)

M3a8 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + FishingMortality + SpawningStockBiomass.1000t + (1 + clogAge|fGrowingYear), data)

M3a9 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC + SpawningStockBiomass.1000t + (1 + clogAge|fGrowingYear), data)

# 3 vars
M3a10 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC + FishingMortality + SpawningStockBiomass.1000t + (1 + clogAge|fGrowingYear), data)


# interaction 1 var Age
M3a11 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC*clogAge + (1 + clogAge|fGrowingYear), data)

M3a12 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + FishingMortality*clogAge + (1 + clogAge|fGrowingYear), data)

M3a13 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SpawningStockBiomass.1000t*clogAge + (1 + clogAge|fGrowingYear), data)

# interaction 2 vars Age
M3a14 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC*clogAge + FishingMortality*clogAge + (1 + clogAge|fGrowingYear), data)

M3a15 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC*clogAge + FishingMortality + (1 + clogAge|fGrowingYear), data)

M3a16 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC + FishingMortality*clogAge + (1 + clogAge|fGrowingYear), data)


M3a17 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC*clogAge + SpawningStockBiomass.1000t*clogAge + (1 + clogAge|fGrowingYear), data)

M3a18 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC*clogAge + SpawningStockBiomass.1000t + (1 + clogAge|fGrowingYear), data)

M3a19 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC + SpawningStockBiomass.1000t*clogAge + (1 + clogAge|fGrowingYear), data)



M3a20 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + FishingMortality*clogAge +  SpawningStockBiomass.1000t*clogAge + (1 + clogAge|fGrowingYear), data)

M3a21 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + FishingMortality +  SpawningStockBiomass.1000t*clogAge + (1 + clogAge|fGrowingYear), data)

M3a22 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + FishingMortality*clogAge +  SpawningStockBiomass.1000t + (1 + clogAge|fGrowingYear), data)

# interaction 3 vars Age
M3a23 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC*clogAge + FishingMortality*clogAge +  SpawningStockBiomass.1000t*clogAge + (1 + clogAge|fGrowingYear), data)

# interaction vars
M3a24 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC*FishingMortality +  SpawningStockBiomass.1000t + (1 + clogAge|fGrowingYear), data)

M3a25 <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + SeaBottomTemperature.degC*SpawningStockBiomass.1000t + FishingMortality + (1 + clogAge|fGrowingYear), data)

# Model comparison
models<-list(M3a2, M3a4, M3a5, M3a6, M3a7, M3a8, M3a9, M3a10, M3a11, M3a12, M3a13, M3a14, M3a15, M3a16, M3a17, M3a18, M3a19, M3a20, M3a21, M3a22, M3a23, M3a24, M3a25)
Modnames <- c('M3a2', 'M3a4', 'M3a5', 'M3a6', 'M3a7', 'M3a8', 'M3a9', 'M3a10', 'M3a11', 'M3a12', 'M3a13', 'M3a14', 'M3a15', 'M3a16', 'M3a17', 'M3a18', 'M3a19', 'M3a20', 'M3a21', 'M3a22', 'M3a23', 'M3a24', 'M3a25') 
aictab(cand.set = models, modnames = Modnames, sort = TRUE)
```

Best model: M4d11 - M4d11 \<- lmer(log(AnnulusDiameterIncrement.um) \~ Age + FishingMortality\*clogAGe + (Age\|FishID) + (Age\|fGrowingYear) + (Age\|fYearclass), data)

```{r}
# Refit with REML 
M3a12.reml <- lmer(log(AnnulusDiameterIncrement.um) ~ clogAge + clogAAC + (1 + clogAge|FishID) + FishingMortality*clogAge + (1 + clogAge|fGrowingYear), data, REML = T)


```

#### 3.1.4. Visualize effect

##### Age

```{r}
df_Age <- unique(select(data, Age, clogAge))

age.plot <- as.data.frame (Effect ('clogAge', M3a12.reml, xlevels = list(clogAge = df_Age$clogAge)))
#age.plot <- as.data.frame (Effect (c('Age'), M4d11.reml, xlevels = list(Age=seq(1,14, by=1))))
age.plot <- age.plot %>% mutate(transfit = exp(fit),
                                transupper = exp(upper),
                                tranlower = exp(lower),
                                Age = df_Age$Age)

ggplot() + 
  geom_point(data = age.plot, aes(x = Age, y = transfit)) +
  geom_errorbar(data = age.plot, aes(x = Age,
                                    ymin = tranlower, 
                                    ymax = transupper), 
                width=.2) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank()) +
  xlab("Age (year)") +
  ylab("Predicted annual growth (µm)")
```

##### Age at capture

```{r}
df_AAC <- unique(select(data, AgeAtCapture, clogAAC))

aac.plot <- as.data.frame (Effect ('clogAAC', M3a12.reml, xlevels = list(clogAAC = df_AAC$clogAAC)))
#age.plot <- as.data.frame (Effect (c('Age'), M4d11.reml, xlevels = list(Age=seq(1,14, by=1))))
aac.plot <- aac.plot %>% mutate(transfit = exp(fit),
                                transupper = exp(upper),
                                tranlower = exp(lower),
                                AgeAtCapture = df_AAC$AgeAtCapture)

ggplot() + 
  geom_ribbon(data = aac.plot, 
              aes(x = AgeAtCapture,
                  ymax = transupper,
                  ymin = tranlower),
             alpha = 0.5) +
  geom_line(data = aac.plot, 
            aes(x = AgeAtCapture, 
                y = transfit),
            size = 1) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank()) +
  xlab("Age At Capture (year)") +
  ylab("Predicted annual growth (µm)") +
  xlim(3,15)
```

##### FishingMortality

```{r}
df_Age <- unique(select(data, Age, clogAge))

f.plot <- as.data.frame (Effect (c('FishingMortality','clogAge'), M3a12.reml, xlevels = list(clogAge = df_Age$clogAge)))

f.plot <- f.plot %>% mutate(transfit = exp(fit),
                            transupper = exp(upper),
                            tranlower = exp(lower),
                            clogAge = as.factor(clogAge)
                            )

df_Age <- df_Age %>% mutate(Age = as.factor(Age),
                            clogAge = as.factor(clogAge))
f.plot <- left_join(f.plot, df_Age, by = "clogAge")


ggplot() +
 geom_ribbon(data = f.plot, 
              aes(x = FishingMortality,
                  ymax = transupper,
                  ymin = tranlower, 
                  fill = Age),
             alpha = 0.5) +
  geom_line(data = f.plot, 
            aes(x = FishingMortality, 
                y = transfit, color = Age),
            size = 1) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank()) +
  xlab("Fishing Mortality") +
  ylab("Predicted annual growth (µm)") +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank()) +
  theme(axis.title = element_text(face = "bold"))
  
```

##### 
